### 2013-02-15 doc/icml2013/evaluation.tex
Updated experiments

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent algorithm\citationneeded. The
algorithm was initialized with the regularized least squares solution
and was run to convergence in each instance. Both regularization
parameters were annealed as $\frac{1}{T}$.

As a baseline, we also implemented EM with two different
initializations. For the first, we used $\beta$s with random standard
Gaussian entries and uniform mixture probabilities, $\pi$. In the other,
we initialized EM with the starting points given by Spectral Experts.

@@

  \begin{tabular}{ >{\centering}p{5cm}<{\centering} r c c c }
\hline
\abovespace\belowspace
Features  & $K$ & Spectral & EM & Spectral + EM \\
\hline
\abovespace
$\{1$, $ x_1$, $ x_1^4\}$ 
  & 2 & 2.54 $\pm$ 2.81 & 0.28 $\pm$ 0.82 & 0.13 $\pm$ 0.55 \\
$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  & 3 & 3.93 $\pm$ 5.82 & 0.33 $\pm$ 0.96 & 0.35 $\pm$ 1.23 \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  & 5 & 5.27 $\pm$ 2.32 & 1.80 $\pm$ 1.80 & 1.51 $\pm$ 1.77 \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2$, $ x_1^3 x_2^4$, $ x_1^4 x_2^3 \}$ 
  & 7 & 8.42 $\pm$ 1.66 & 7.41 $\pm$ 2.99 & 7.31 $\pm$ 2.47 \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
  & 3 & 3.78 $\pm$ 0.90 & 0.67 $\pm$ 1.49 & 0.51 $\pm$ 1.12 \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
  & 7 & 9.97 $\pm$ 3.22 & 1.43 $\pm$ 1.97 & 1.42 $\pm$ 2.17 \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table*}

\todo{Dataset 2: $b = 30$, $p = 1$. I'm unclear as to what we can show
on this sort of data set. EM works extremely well, and the spectral
methods do not converge easily.}

@@

\paragraph{Basic results}

Punchline: spectral by itself is medicore, offers a good initialization to EM.
EM with random initialization is much less stable. (by table)

Using canonical settings, on the various datasets: \tableref{tbl:parameter-recovery}.

Plot: the histogram over errors (for EM?) \todo{Some plots I have doesn't really show much}.

@@

To show how well spectral methods can handle mis-specification, we
compared the performance of the different algorithms with entire
segments removed from the generated data. \todo{Table X shows figures}.

\paragraph{Effect on number of data points}

@@

>>>>

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent algorithm\citationneeded. The
algorithm was initialized with the regularized least squares solution
and was run to convergence in each instance. Both regularization
parameters, $\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as
$\frac{1}{n}$.

As a baseline, we also implemented EM with two different
initializations. In the first, we used $\beta$s with random standard
Gaussian entries and uniform mixture probabilities, $\pi$. In the other,
we initialized EM with the starting points given by Spectral Experts.

@@

  \begin{tabular}{ >{\centering}p{5cm}<{\centering} r c c c }
\hline
\abovespace\belowspace
Features  & $K$ & Spectral & EM & Spectral + EM \\
\hline
\abovespace
$\{1$, $ x_1$, $ x_1^4\}$ 
  & 2 & 1.52 $\pm$ 0.71 & 0.28 $\pm$ 0.82 & {\bf 0.13 $\pm$ 0.55} \\
$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  & 3 & 1.87 $\pm$ 1.20 & {\bf 0.33 $\pm$ 0.96} & 0.35 $\pm$ 1.23 \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
& 5 & 5.27 $\pm$ 2.32 & 1.80 $\pm$ 1.80 & {\bf 1.51 $\pm$ 1.77} \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2$, $ x_1^3 x_2^4$, $ x_1^4 x_2^3 \}$ 
& 7 & 8.42 $\pm$ 1.66 & 7.41 $\pm$ 2.99 & {\bf 7.31 $\pm$ 2.47} \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
& 3 & 3.78 $\pm$ 0.90 & 0.67 $\pm$ 1.49 & {\bf 0.51 $\pm$ 1.12} \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
  & 7 & 9.97 $\pm$ 3.22 & 1.43 $\pm$ 1.97 & {\bf 1.42 $\pm$ 2.17} \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table*}

% \todo{Dataset 2: $b = 30$, $p = 1$. I'm unclear as to what we can show
% on this sort of data set. EM works extremely well, and the spectral
% methods do not converge easily.}

@@

\tableref{tbl:parameter-recovery} presents the Fro\"ebenius norm of the
difference between true and estimated parameters for the model, averaged
over 20 different random instances for each feature set and 10 attempts
for each instance. The experiments were run using $N = 500,000$ samples.

There is a lot of variation across random instances; some are easy for
EM to find the global minima and others more difficult. Moreover, simply
increasing the number of samples did not necessarily improve EM
performance. In general, we found that while our spectral algorithm did
not recover parameters extremely well, it provided a good initialization
for EM.

\todo{Plot: the histogram over errors (for EM?) Some plots I have
doesn't really show much}.

@@

To evaluate how robust the algorithm was to model mis-specification, we
removed large contiguous sections from $x \in [-0.5,-0.25] \cup
[0.25,0.5]$. The lower half of \tableref{tbl:parameter-recovery} reports
recovery errors in this scenario.

\paragraph{Effect of number of data points}

@@

Highlight
